---
title: "Define Study Area"
subtitle: "Working scope and the next design decisions"
output:
  html_document:
    self_contained: true
    mathjax: null
params:
  report: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = TRUE)
r <- params$report
esc <- function(x) {
  x <- gsub('&', '&amp;', x, fixed = TRUE)
  x <- gsub('<', '&lt;', x, fixed = TRUE)
  gsub('>', '&gt;', x, fixed = TRUE)
}
tab <- function(x) cat(as.character(knitr::kable(x,
  format = 'html', escape = TRUE, row.names = FALSE)))
count <- function(x) if (is.null(x)) 0L else nrow(x)
reach_counts <- if (count(r$streams)) vapply(r$streams$stream_id, function(id)
  if (!count(r$reaches)) 0L else sum(r$reaches$stream_id == id), integer(1)) else integer()
```

## What is known

This is a working study definition, not approval of its scope or readiness for
analysis. It can begin before a boundary, terrain or survey has been acquired.

```{r known, results='asis'}
tab(data.frame(Item = c('Working Study Area name', 'Boundary', 'Selected Streams',
  'Defined Reaches', 'Recorded Survey Events'),
  Description = c(if (is.null(r$study_area)) 'Not yet named' else r$study_area$study_area_name,
    if (inherits(r$study_area, 'sf')) 'Supplied; review its suitability for the intended scope' else 'Not yet supplied; no extent inferred',
    if (!count(r$streams)) 'Not yet specified' else paste(nrow(r$streams), 'explicitly named; inventory below'),
    if (!count(r$reaches)) 'Not yet specified' else as.character(nrow(r$reaches)),
    if (!count(r$surveys)) 'None recorded; this does not imply none are planned' else as.character(nrow(r$surveys)))))
```

```{r stream-inventory, results='asis'}
if (count(r$streams)) {
  cat('### Selected Streams\n\n')
  tab(data.frame(Stream = seq_len(nrow(r$streams)), Name = r$streams$stream_name,
    Area = if (inherits(r$streams, 'sf')) 'Supplied; suitability remains for review' else 'Not yet supplied',
    Reaches = ifelse(reach_counts == 0L, 'Not yet defined', as.character(reach_counts))))
}
```

```{r reach-inventory, results='asis'}
if (count(r$reaches)) {
  cat('### Defined Reaches\n\n')
  tab(data.frame(Reach = seq_len(nrow(r$reaches)),
    Stream = r$streams$stream_name[match(r$reaches$stream_id, r$streams$stream_id)],
    Name = r$reaches$reach_name,
    Area = if (inherits(r$reaches, 'sf')) 'Supplied; suitability remains for review' else 'Not yet supplied'))
  cat('<p>This is the recorded inventory; a listed Reach does not establish that its Stream has been fully divided.</p>')
}
```

```{r survey-inventory, results='asis'}
if (count(r$surveys)) {
  cat('### Recorded Survey Events\n\n')
  ri <- match(r$surveys$reach_id, r$reaches$reach_id)
  source <- if ('source_dataset' %in% names(r$surveys)) r$surveys$source_dataset else rep(NA_character_, count(r$surveys))
  tab(data.frame(Stream = r$reaches$stream_name[ri], Reach = r$surveys$reach_name,
    Acquisition = r$surveys$date_label,
    Precision = ifelse(is.na(r$surveys$survey_month), 'Year only', ifelse(is.na(r$surveys$survey_day), 'Month', 'Day')),
    `Source reference` = ifelse(is.na(source), 'Not recorded', source), check.names = FALSE))
  cat('<p>Recorded acquisition evidence is not a verified terrain-file link or proof of comparability. Event evidence notes and saved identities are in the Supporting record.</p>')
}
```

```{r event-terrain, results='asis'}
if (count(r$event_artifacts)) {
  cat('### Associated terrain files\n\n')
  links <- r$event_artifacts
  si <- match(links$survey_event_id, r$surveys$survey_event_id)
  files <- r$folder_inventory$artifacts
  ai <- match(links$artifact_id, files$artifact_id)
  tab(data.frame(Reach = r$surveys$reach_name[si], Acquisition = r$surveys$date_label[si],
    File = links$path,
    `File fingerprint` = ifelse(files$hash_verified[ai], 'Matches snapshot', 'Missing or changed'),
    `Grid preview` = ifelse(links$grid_status == 'GRID_LOADED', 'Available',
      ifelse(links$grid_status == 'NOT_SELECTED', 'Not selected', 'Not loaded; review findings')),
    `Vertical reference / unit` = paste(ifelse(is.na(files$vertical_reference[ai]), 'Unknown', files$vertical_reference[ai]),
      ifelse(is.na(files$vertical_unit[ai]), 'Unknown', files$vertical_unit[ai]), sep = ' / '), check.names = FALSE))
  cat('<p>Association and matching fingerprints do not establish terrain suitability. Preview availability concerns grid metadata, not comparability. NoData masking can deliberately define the area of interest; its percentage is not a quality score. Review unresolved findings in the Supporting record.</p>')
}
```

### Purpose and scope notes

```{r notes, results='asis'}
if (is.na(r$analyst_notes)) {
  cat('<p>Not yet recorded. Start with the customer question and intended use of the results.</p>')
} else cat('<div style="white-space: pre-wrap">', esc(r$analyst_notes), '</div>', sep = '')
```

```{r boundary-heading, results='asis'}
if (inherits(r$study_area, 'sf')) {
  cat('## Working Study Area extent\n\nThe boundary is analyst supplied, not an approved scope or a derived watershed. Review the location and shape against the customer question. No online basemap is required.\n\n')
} else if (inherits(r$streams, 'sf')) cat('## Selected Stream areas\n\nNo Study Area boundary has been inferred from these areas.\n\n') else if (inherits(r$reaches, 'sf')) cat('## Supplied Reach areas\n\nNo Study Area boundary has been inferred from these areas.\n\n')
```

```{r boundary-map, fig.width=8, fig.height=5, fig.alt='Supplied Study Area, Stream and Reach areas; only available geometry is shown'}
if (inherits(r$study_area, 'sf') || inherits(r$streams, 'sf') || inherits(r$reaches, 'sf')) {
  crs <- sf::st_crs(if (inherits(r$study_area, 'sf')) r$study_area else if (inherits(r$streams, 'sf')) r$streams else r$reaches)
  p <- ggplot2::ggplot()
  if (inherits(r$streams, 'sf')) {
    areas <- r$streams
    areas$stream_key <- factor(seq_len(nrow(areas)))
    p <- p + ggplot2::geom_sf(data = areas, ggplot2::aes(fill = stream_key), colour = 'white', linewidth = 0.3)
  }
  if (inherits(r$study_area, 'sf')) p <- p + ggplot2::geom_sf(data = r$study_area,
    fill = if (inherits(r$streams, 'sf')) NA else '#e8eef3', colour = '#1d3038')
  if (inherits(r$reaches, 'sf')) {
    reach_areas <- r$reaches
    reach_areas$reach_key <- factor(seq_len(nrow(reach_areas)))
    p <- p + ggplot2::geom_sf(data = reach_areas, ggplot2::aes(colour = reach_key),
      fill = NA, linewidth = 1, linetype = 'dashed')
  }
  print(p +
    ggplot2::coord_sf(crs = crs, datum = crs) +
    ggplot2::scale_x_continuous(n.breaks = 3) +
    ggplot2::theme_minimal(base_size = 12) +
    ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1), legend.position = 'bottom') +
    ggplot2::labs(x = NULL, y = NULL, fill = 'Stream number', colour = 'Reach number (dashed)',
      caption = paste('Display CRS:', crs$Name, '| Units:', crs$units_gdal)))
}
```

## What to decide next

These are design conversations, not a mandatory sequence or compliance failures.
Record decisions and unresolved alternatives as customer requirements develop.

```{r next, results='asis'}
tasks <- character()
if (is.na(r$analyst_notes)) tasks <- c(tasks, 'Describe the customer question, intended decisions and initial scope in an analyst note.')
if (!inherits(r$study_area, 'sf')) tasks <- c(tasks, 'Discuss the candidate Study Area extent and why it fits the customer question; supply a boundary when ready.')
if (!count(r$streams)) tasks <- c(tasks, 'Choose the Streams to include and explain the naming and segmentation basis; HUC boundaries are optional.')
if (!count(r$reaches)) tasks <- c(tasks, 'Agree on meaningful Reach divisions within the selected Streams.')
if (count(r$reaches) && any(reach_counts == 0L)) tasks <- c(tasks, paste(
  'Reach definitions remain open for:', paste(r$streams$stream_name[reach_counts == 0L], collapse = ', ')))
if (count(r$reaches) && !inherits(r$reaches, 'sf')) tasks <- c(tasks,
  'Reach names and parent Streams are recorded; their spatial extent is not yet supplied as a polygon. Decide whether an area is useful for scope review; its absence alone does not prevent analysis.')
if (!count(r$surveys)) tasks <- c(tasks, 'Discuss intended observations and periods in the scope notes. Add Survey Event records only when actual acquisition evidence is available.')
selected_events <- if (count(r$event_artifacts)) r$event_artifacts$survey_event_id[r$event_artifacts$use_for_report] else character()
if (count(r$surveys) && any(!r$surveys$survey_event_id %in% selected_events)) tasks <- c(tasks, 'Review source evidence and associate the intended terrain files with each event before comparing periods. Record additional plans separately; this inventory does not establish completeness or comparability.')
if (count(r$event_artifacts)) tasks <- c(tasks, 'Resolve file-integrity or metadata findings, confirm elevation units and vertical reference, then review suitability for the intended comparison. Associated terrain is not yet approved for analysis.')
if (!length(tasks)) tasks <- 'Review whether the supplied scope and its rationale still answer the customer question; table presence alone does not establish completeness.'
cat('<ul>', paste0('<li>', esc(tasks), '</li>', collapse = ''), '</ul>')
```

The current starter, name/note editor, boundary, initial Stream-definition and
Reach-addition, Reach-area and acquired-event tools capture the beginning of this process. Existing identity
renaming/removal, mixed missing/supplied Reach areas, structured alternatives and planned campaigns
are not yet offered by these QGIS forms. No legacy archive or FileGDB staging
step is required for a new project. Terrain suitability is reviewed separately.

## Supporting record

<details>
<summary>Saved identity and supplied inventory</summary>

```{r record, results='asis'}
for (entry in c('study_area', 'streams', 'reaches', 'surveys')) {
  x <- r[[entry]]
  if (!count(x)) next
  cat('<h3>', c(study_area = 'Study Area', streams = 'Streams', reaches = 'Reaches', surveys = 'Survey Events')[[entry]], '</h3>')
  tab(as.data.frame(sf::st_drop_geometry(x)))
}
cat('<p>Snapshot: ', esc(format(r$generated_at, tz = 'UTC', usetz = TRUE)), '</p>', sep = '')
```

Keep the context GeoPackage as the editable record. The starter creates a new
local identity; it does not register or reconcile a Study Area in FGDB. Reopen
and revise that context instead of starting it again under a second identity.
Supplied notes are analyst statements, not independently verified facts.
Changing report purpose does not change saved records or approve a study.

</details>

```{r terrain-record, results='asis'}
if (!is.null(r$folder_inventory)) {
  cat('<details><summary>Terrain associations and review findings</summary>')
  if (count(r$event_artifacts)) tab(r$event_artifacts)
  findings <- r$assessment[r$assessment$stage %in% c('FILE_INTEGRITY', 'EVENT_ASSOCIATION'), , drop = FALSE]
  if (nrow(findings)) tab(findings)
  tab(r$folder_inventory$artifacts)
  cat('</details>')
}
```
