---
title: "FluvialGeomorph Level 2 Report"
params:
  stream: ""
  flowline_sf:  ""
  xs_sf: ""
  xs_dims_sf: ""
  xs_pts_sf_list: ""
  features_sf: ""
  channel_sf: ""
  floodplain_sf: ""
  dem: ""
  bf_estimate: ""
  regions: ""
  label_xs: TRUE
  show_xs_map: FALSE
  profile_units: "kilometers"
  aerial: TRUE
  elevation: FALSE
  xs_label_freq: 5
  exaggeration: 10
  extent_factor: 1.1
  output_format: "word_document"
output: 
  word_document:
    reference_docx: word_template.docx
---

```{r library, eval=TRUE, include=FALSE}
library(fluvgeo)
library(sf)
library(dplyr)
library(knitr)
library(ggplot2)
library(ggrepel)
library(patchwork)
library(tmap)
library(terra)
library(terrainr)
```

## Study Area Overview: `r params$stream`
```{r aerial_overview, echo=FALSE, warning=FALSE, message=FALSE, results="hide", fig.width=7, fig.height=7, fig.cap="Reach Overview Map"}
if(params$show_xs_map & params$aerial) {
  print(fluvgeo::map_reach_overview(flowline = params$flowline_sf, 
                                    cross_section = params$xs_dims_sf,
                                    background = "aerial",
                                    xs_label_freq = params$xs_label_freq,
                                    extent_factor = params$extent_factor))
}
```

```{r elevation_overview, echo=FALSE, warning=FALSE, message=FALSE, results="hide", fig.width=7, fig.height=7, fig.cap="Reach Overview Map"}
if(params$show_xs_map & params$elevation) {
  print(fluvgeo::map_reach_overview(flowline = params$flowline_sf, 
                                    cross_section = params$xs_dims_sf,
                                    background = "elevation",
                                    xs_label_freq = params$xs_label_freq,
                                    extent_factor = params$extent_factor))
}
```

## Longitudinal Profile
```{r, longitudinal_profile_plot, eval=TRUE, echo=FALSE, results='asis', fig.width=7, fig.height=7, fig.cap="Longitudinal Profile Plot"}

print(fluvgeo::xs_profile_plot(reach_xs_dims = xs_dims_sf, 
                               features = features_sf, 
                               label_xs = params$label_xs,
                               xs_label_freq = params$xs_label_freq,
                               profile_units = params$profile_units))
```

## Cross Section Metrics
```{r, xs_metrics_plot, eval=TRUE, echo=FALSE, results='asis', fig.width=7, fig.height=9, fig.cap="Cross Section Metrics Plot. ", warning=FALSE}
print(fluvgeo::xs_metrics_plot_L2(xs_dims_sf = params$xs_dims_sf, 
                                  features_sf = params$features_sf,
                                  label_xs = params$label_xs,
                                  xs_label_freq = params$xs_label_freq,
                                  profile_units = params$profile_units))
```

## Width Depth Ratio
```{r, wdr, echo=FALSE}
# Create the fluvgeo::FluvialGeomorphicMetric object
wdr <- new(Class = "FluvialGeomorphicMetric",
           metric = "Width Depth Ratio",
           definition = "bankfull width / bankfull depth",
           variable = "xs_width_depth_ratio",
           threshold_breaks = c(0, 10, 20, Inf),
           threshold_labels = c("Incised",
                                "Stable",
                                "Overwidened"),
           source = "Dunn & Leopold, 1978")
```

```{r, wdr_map, eval=TRUE, echo=FALSE, results='asis', fig.width=7, fig.height=8, fig.cap="Width depth Ratio Map", warning=FALSE, message=FALSE}
if(params$show_xs_map) {
  # Set background
  if(params$aerial & params$elevation)   {background <- "aerial"}
  if(params$aerial & !params$elevation)  {background <- "aerial"}
  if(!params$aerial & params$elevation)  {background <- "elevation"}
  if(!params$aerial & !params$elevation) {background <- "none"}
  print(fluvgeo::map_reach_metric(wdr,
                                  flowline = params$flowline_sf,
                                  xs_label_freq = params$xs_label_freq,
                                  xs_dimensions = params$xs_dims_sf,
                                  background = background))
}
```

```{r wdr_plot, eval=TRUE, echo=FALSE, fig.width=7, fig.cap="Width Depth Ratio Graph", warning=FALSE}
print(fluvgeo::xs_metric_plot(metric = wdr,
                              reach_xs_dims = params$xs_dims_sf,
                              label_xs = TRUE,
                              xs_label_freq = params$xs_label_freq,
                              profile_units = params$profile_units))
```

## Cross Section Geometry
The figure below displays the selected regional hydraulic geometry curves plotted with the values for each of the cross sections in the current reach.

```{r, regional_curve_graph, eval=TRUE, echo=FALSE, results='asis', fig.width=7, fig.height=8, fig.cap="Regional Hydraulic Geometry Curves"}
# Calculate cross section dimensions
xs_pts <- params$xs_pts_sf_list[[1]]

# Calculate cross section dimensions for the reach regional curves graph
xs_dims <- xs_dimensions(xs_points = xs_pts,
                         streams = params$stream,
                         regions = params$regions,
                         bankfull_elevations = c(params$bf_estimate))

# Draw reach regional curves graph
print(fluvgeo::reach_rhg_graph(xs_dims = xs_dims,
                               streams = params$stream,
                               bf_elevation = params$bf_estimate))
```

## Cross Section Profiles
This section displays cross section profile graphs for each riffle cross section in this stream reach. A table of cross section hydraulic geometry dimensions appears under each cross section profile. The first row contains the hydraulic geometry dimensions for the the current cross section, while subsequent rows contain hydraulic geometry dimensions for selected regions.

```{r cross_section_plots, echo=FALSE, results='asis',fig.width=7, fig.height=10, warning=FALSE, error=FALSE, message=FALSE}
# Get dem raster
dem_rast <- fluvgeo::gdb_raster2SpatRast(raster_path = params$dem)

# Ensure that cross sections are sequentially ordered
cross_section <- dplyr::arrange(params$xs_sf, Seq)

# Iterate through cross sections
for(j in unique(cross_section$Seq)) {
  # Create cross section profiles plot
  print(fig_xs_profiles_L2(cross_section = cross_section,
                           xs_number = j,
                           dem = dem_rast,
                           channel = params$channel_sf,
                           floodplain = params$floodplain_sf,
                           bf_estimate = params$bf_estimate,
                           regions = params$regions,
                           extent_factor = params$extent_factor,
                           xs_pts_sf_list = params$xs_pts_sf_list))
  # Insert vertical white space so that next figure in loop is recognized
  cat('\n')
  # Must set chunk option`results='asis'` to ensure table is drawn properly
}
```


version 0.1.48
