---
title: "Study Area Staging Report"
subtitle: "Project structure, source evidence and the next analyst decisions"
output:
  html_document:
    self_contained: true
    mathjax: null
    toc: true
    toc_depth: 2
params:
  report: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = TRUE)
r <- params$report
esc <- function(x) {
  x <- gsub('&', '&amp;', x, fixed = TRUE)
  x <- gsub('<', '&lt;', x, fixed = TRUE)
  gsub('>', '&gt;', x, fixed = TRUE)
}
tab <- function(x, fields = names(x)) {
  if (is.null(x) || !nrow(x)) return(cat('<p>No records supplied.</p>'))
  cat(as.character(knitr::kable(as.data.frame(sf::st_drop_geometry(x))[intersect(fields, names(x))],
    format = 'html', escape = TRUE, row.names = FALSE)))
}
# A view selection only: the supplied summary and its full assessment are unchanged.
actions <- r$review_actions
if (!is.null(actions)) actions <- actions[actions$stage != 'TERRAIN_REVIEW', , drop = FALSE]
```

## What is known

This report asks whether the project structure is explicitly specified and what
an analyst must still resolve. It is not a terrain-quality assessment, a
conversion certificate or FGDB load approval. The Terrain Development Report
addresses terrain sources, processing and scientific limitations separately.

```{r known, results='asis'}
tab(data.frame(Item = c('Study Area', 'Selected Streams', 'Defined Reaches', 'Survey Events', 'Study Area boundary'),
  Evidence = c(if (is.null(r$study_area)) 'Not supplied' else r$study_area$study_area_name,
    if (is.null(r$streams)) 'Not supplied' else paste(r$streams$stream_name, collapse = ', '),
    if (is.null(r$reaches)) 'Not supplied as explicit records' else as.character(nrow(r$reaches)),
    if (!nrow(r$surveys)) 'No dated event records supplied; no dates inferred' else as.character(nrow(r$surveys)),
    if (inherits(r$study_area, 'sf')) 'Supplied AOI; see interpretation evidence' else 'Not supplied; no boundary inferred')))
if (!is.na(r$analyst_notes)) {
  cat(paste0('<p>', esc(strsplit(r$analyst_notes, '\n[[:space:]]*\n', perl = TRUE)[[1]]), '</p>', collapse = '\n'))
}
if (!is.null(r$staging_inventory)) {
  g <- r$staging_inventory$geodatabases
  cat('<p><strong>Inspected staging:</strong> ', nrow(g), ' geodatabase directories; ',
    sum(g$listing_status != 'UNREADABLE'), ' vector/table listings obtained. ',
    'These are source containers, not confirmed Survey Events. Rasters are not inspected.</p>', sep = '')
}
cat('<p><small>Snapshot: ', esc(format(r$generated_at, tz = 'UTC', usetz = TRUE)), '</small></p>', sep = '')
```

## What the analyst needs to do next

Repeated prompts are grouped for readability, not permission to make one decision
for every affected source. Required scientific interpretations remain human
decisions; mechanical catalog entry and integrity checks should be automated.

```{r next, results='asis'}
if (is.null(actions) || !nrow(actions)) {
  cat('<p>No pending staging prompts in this supplied assessment. This does not establish readiness.</p>')
} else tab(data.frame(Work = ifelse(actions$requires_input, 'Analyst input', 'Further validation'),
  Status = actions$status, `Affected references` = actions$entity_count,
  `Next action` = actions$next_action, check.names = FALSE))
pending <- r$reconstruction
if (!is.null(pending)) pending <- pending[pending$status %in% c('UNKNOWN', 'PROPOSED'), , drop = FALSE]
if (!is.null(pending) && nrow(pending)) {
  cat('<h3>Specific unresolved interpretations</h3>')
  tab(pending, c('source_ref', 'evidence', 'proposed_structure', 'status'))
}
```

## Study structure and boundary

Only supplied parent relationships are shown. Staged folder names do not create
identities or Survey Events. A Study Area and its sole Stream may share a boundary
while retaining distinct identities.

```{r structure, fig.width=10, fig.height=max(3, 0.55 * nrow(r$hierarchy)), fig.cap='Supplied geographic hierarchy; no relationships inferred from staging paths.'}
h <- r$hierarchy
if (!is.null(h)) h <- h[h$entity_type %in% c('Study Area', 'Stream', 'Reach', 'Survey Event'), , drop = FALSE]
if (!is.null(h) && nrow(h)) {
  h$y <- rev(seq_len(nrow(h)))
  h$text <- vapply(paste(h$entity_type, h$label, sep = ': '),
    function(x) paste(strwrap(x, width = 28), collapse = '\n'), character(1))
  edges <- h[!is.na(h$parent_key) & h$parent_key %in% h$node_key, , drop = FALSE]
  parents <- match(edges$parent_key, h$node_key)
  edges$x0 <- h$depth[parents]; edges$y0 <- h$y[parents]
  print(ggplot2::ggplot(h, ggplot2::aes(x = depth, y = y)) +
    ggplot2::geom_segment(data = edges, ggplot2::aes(x = x0, y = y0, xend = depth, yend = y), colour = '#aab8bf') +
    ggplot2::geom_point(size = 3, colour = '#254c59') +
    ggplot2::geom_label(ggplot2::aes(label = text), hjust = 0, nudge_x = 0.07, size = 3.4) +
    ggplot2::scale_x_continuous(limits = c(-0.1, max(h$depth) + 1.4)) +
    ggplot2::scale_y_continuous(expand = ggplot2::expansion(add = 0.8)) + ggplot2::theme_void())
} else cat('No explicit hierarchy supplied. Source folders remain inventory only.')
```

```{r boundary, fig.width=9, fig.height=6, fig.cap='Supplied Study Area (solid) and Stream (dotted) boundaries. Coincidence is a supplied interpretation, not inferred parentage.'}
if (inherits(r$study_area, 'sf') || inherits(r$streams, 'sf')) {
  p <- ggplot2::ggplot()
  if (inherits(r$study_area, 'sf')) p <- p + ggplot2::geom_sf(data = r$study_area, fill = '#edf3f0', colour = '#203b48')
  if (inherits(r$streams, 'sf')) p <- p + ggplot2::geom_sf(data = r$streams, fill = NA, colour = '#54816b', linetype = 'dotted')
  print(p + ggplot2::theme_minimal() + ggplot2::labs(x = NULL, y = NULL))
} else cat('No supplied polygon available for mapping.')
```

## Supporting record

<details open>
<summary>Streams, Reaches and Survey Event inventory</summary>

```{r hierarchy-inventory, results='asis'}
cat('<h3>Streams</h3>'); tab(r$streams, 'stream_name')
cat('<h3>Reaches</h3>'); tab(r$reaches, c('stream_name', 'reach_name'))
cat('<h3>Survey Events</h3>'); tab(r$surveys, c('reach_name', 'date_label', 'source_dataset', 'availability_notes'))
```

</details>

<details>
<summary>Source containers and catalog presence</summary>

Presence is not validation of fields, values, geometry or parent references.
Missing records refer to staging draft 0.1, not a historical archive requirement.

```{r source-record, results='asis'}
if (!is.null(r$staging_inventory)) {
  tab(r$staging_inventory$geodatabases)
  cat('<h3>Expected catalog records</h3>')
  x <- r$staging_inventory$catalogs
  x$present <- ifelse(is.na(x$present), 'Unknown: not inspected or unreadable',
    ifelse(x$present, 'Present; values not validated', 'Not found'))
  tab(x)
  cat('<details><summary>Driver-reported vector/table layers</summary><p>Unknown feature counts are not zero. Z/M types are reported, not validated. Raster content is outside this listing.</p>')
  tab(r$staging_inventory$layers)
  cat('</details>')
} else cat('<p>No staging inspection supplied.</p>')
```

</details>

<details>
<summary>Interpretations and analyst decisions</summary>

Confirmed means analyst-confirmed interpretation, not independent verification
or enterprise acceptance. Proposed and unknown interpretations remain separate.

```{r decisions, results='asis'}
tab(r$reconstruction)
```

</details>

<details>
<summary>Detailed staging findings and evidence limits</summary>

```{r findings, results='asis'}
if (!is.null(r$assessment)) tab(r$assessment[r$assessment$stage != 'TERRAIN_REVIEW', , drop = FALSE])
```

The source inventory does not verify rasters, acquisition dates, clean-source
selection, complete catalog values, archive-copy equality or conversion mappings.
Missing evidence is not fabricated. Rendering changes no source data or decisions.

</details>
