---
title: "Survey opportunities"
subtitle: "Additional observations for change-over-time analysis"
output:
  html_document:
    self_contained: true
    mathjax: null
params:
  report: null
  terrain_template: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=TRUE, error=FALSE)
r <- params$report
x <- sf::st_drop_geometry(r$records)
esc <- function(z) gsub('>', '&gt;', gsub('<', '&lt;', gsub('&', '&amp;', z, fixed=TRUE), fixed=TRUE), fixed=TRUE)
tab <- report_table
```

## 1. What is known

```{r report-table-style, results='asis'}
cat('<style>',report_table_css,'</style>',sep='\n')
```

```{r scope, results='asis'}
tab(data.frame(Item=c('Study Area','Review focus','Existing observations','Catalog records supplied','Report generated'),
  Description=c(r$study_area$study_area_name, r$focus_label,
  paste(nrow(r$survey_events),'records; inventory may be incomplete'),
  paste(nrow(x),'listings, NOT independent surveys'),r$generated_at)))
tab(r$survey_events[c('label','date_label')])
```

This is a source-discovery review, not confirmation of provenance or scientific
comparability. Year/month intervals preserve the precision supplied; they do not
claim exact acquisition days. A newly cataloged dataset is not necessarily a new
survey. Planned collections are not observations.

## 2. What to review next

```{r next, results='asis'}
active <- !x$classification %in% c('OUTSIDE_FOCUS','REPRESENTED','REISSUE','DISMISSED','REVIEW_LOCATION')
q <- x[active, , drop=FALSE]
q <- q[order(q$collection_start,na.last=TRUE), , drop=FALSE]
if (nrow(q)) {
  tab(data.frame(Ref=q$review_id, Catalog=q$catalog, Collection=q$title,
    Acquired=q$date_label, Finding=gsub('_',' ',q$classification),
    Footprint=gsub('_',' ',q$spatial_relation), Next=q$next_action))
} else cat('<p>No unreviewed in-focus candidates in this snapshot. This is not proof that no additional surveys exist.</p>')
if (any(x$classification=='REVIEW_LOCATION')) cat('<p>',sum(x$classification=='REVIEW_LOCATION'),
  'catalog footprints need a technical location check. They remain in the supporting record and are not counted as in-focus candidates.</p>')
```

Catalog entries may duplicate the same acquisition. Matching names, years or
footprints are clues, not identity. Confirm data access, source relationships,
vertical references, processing assumptions and uncertainty before proposing analysis.
Footprints are catalog representations, not guarantees of usable terrain coverage.

```{r terrain-review, results='asis'}
if (!is.null(r$terrain_review)) {
  stopifnot(length(params$terrain_template)==1L,file.exists(params$terrain_template))
  cat(knitr::knit_child(params$terrain_template,envir=environment(),quiet=TRUE),sep='\n')
}
```

## 3. Observation periods and candidates

```{r timeline, fig.width=10, fig.height=7}
events <- r$survey_events
dated <- !is.na(x$collection_start) & !is.na(x$collection_end) & active
z <- data.frame(label=c(events$label, paste(x$review_id[dated],x$catalog[dated])),
  start=c(events$collection_start,x$collection_start[dated]),
  end=c(events$collection_end,x$collection_end[dated]),
  type=c(rep('Recorded',nrow(events)), ifelse(x$status[dated]=='PLANNED','Planned','Candidate')))
z <- z[!is.na(z$start) & !is.na(z$end), , drop=FALSE]
if (nrow(z)) {
  z$label <- factor(z$label, levels=rev(unique(z$label)))
  p <- ggplot2::ggplot(z, ggplot2::aes(x=start,xend=end,y=label,yend=label,color=type)) +
    ggplot2::geom_segment(linewidth=2) + ggplot2::geom_point(size=2) +
    ggplot2::scale_color_manual(values=c(Recorded='#243b53',Candidate='#007c83',Planned='#9a6700')) +
    ggplot2::labs(x='Acquisition interval (not publication date)',y=NULL,color=NULL) +
    ggplot2::theme_minimal(base_size=11)
  print(p)
} else cat('No known acquisition intervals to plot.')
```

Undated records remain in the review table. Several bars can describe one acquisition;
this is not a count of independent observations.

## 4. Where the catalog footprints fall

```{r map, fig.width=10, fig.height=7}
valid <- sf::st_is_valid(r$records)
draw <- which(!is.na(valid) & valid & !sf::st_is_empty(r$records) &
  x$spatial_relation %in% c('OUTSIDE_FOCUS','COVERS_FOCUS','INTERSECTS_FOCUS'))
bb <- sf::st_bbox(r$study_area)
p <- ggplot2::ggplot() +
  ggplot2::geom_sf(data=r$study_area,fill='#f3f4f6',color='#243b53',linewidth=0.8)
if (length(draw)) p <- p + ggplot2::geom_sf(data=sf::st_transform(r$records[draw,],sf::st_crs(r$study_area)),
  ggplot2::aes(color=catalog),fill=NA,alpha=0.7,linewidth=0.5)
p <- p + ggplot2::geom_sf(data=r$focus,fill=NA,color='#b42318',linewidth=1) +
  ggplot2::scale_color_viridis_d(end=0.75) +
  ggplot2::coord_sf(xlim=c(bb[['xmin']],bb[['xmax']]),ylim=c(bb[['ymin']],bb[['ymax']])) +
  ggplot2::labs(color='Catalog',caption='Red: review focus. Dark boundary: Study Area. Catalog boundaries are not authoritative.') +
  ggplot2::theme_minimal(base_size=11)
print(p)
```

Invalid/empty footprints are reported, not silently repaired or drawn. A listing
elsewhere in the Study Area is not automatically an opportunity for the focus Reach.

## 5. Search scope and limitations

```{r searches, results='asis'}
tab(r$searches)
```

COMPLETE means the stated query completed, not that a catalog covers every source.
PARTIAL, FAILED and NOT_SEARCHED require follow-up. Retrieval dates identify the
snapshots reviewed; no automatic refresh or background monitoring occurs.

<details>
<summary>Supporting record: all listings and supplied review evidence</summary>

```{r supporting, results='asis'}
for (i in seq_len(nrow(x))) {
  cat('<h4>',esc(paste(x$review_id[i],x$title[i])),'</h4>')
  cols <- c('catalog','record_id','snapshot_id','date_label','status','spatial_relation',
    'classification','next_action','source_group','identity_evidence','disposition',
    'event_id','review_note','metadata_url')
  tab(data.frame(Field=cols,Value=as.character(unlist(x[i,cols],use.names=FALSE))))
}
```

</details>
