### Terrain references: what is known

File declarations, the chosen analysis reference, and the preparation history
answer different questions. Source and analysis CRS may legitimately differ.
None of the observations below automatically confirms lineage or accepts terrain
for change-over-time analysis.

```{r terrain-files, results='asis'}
tab <- report_table
tr <- r$terrain_review
f <- tr$files
for (role in c('SOURCE_PRODUCT','ANALYSIS_DEM')) {
  z <- f[f$role==role,,drop=FALSE]
  cat('<h4>',if (role=='SOURCE_PRODUCT') 'Selected source products' else 'Selected analysis DEMs','</h4>')
  if (nrow(z)) tab(data.frame(Artifact=z$label, Horizontal=z$horizontal,
    Vertical=z$vertical, 'Vertical CRS unit'=z$vertical_unit, check.names=FALSE))
  else cat('<p>None selected for this review.</p>')
}
```

“Not exposed” does not prove that metadata is absent. A file declaration is not
proof that its elevations were processed correctly. These are file-level
observations, not a quality score or an assessment of intentional NoData masking.

#### Chosen project analysis reference

```{r terrain-analysis-choice, results='asis'}
a <- tr$analysis_reference
component <- c(horizontal='Horizontal reference',vertical='Vertical reference',elevation_unit='Elevation unit')
basis <- c(UNRESOLVED='Not yet recorded',PROJECT_RECORD='Supplied project record',
  OWNER_RECOLLECTION='Owner recollection',PROPOSED='Proposed; not established')
tab(data.frame(Component=unname(component[a$component]),
  Choice=ifelse(is.na(a$value),'Not yet recorded',a$value),
  Basis=unname(basis[a$basis])))
```

Preparing project DEMs in a common analysis reference can avoid repeated
transformations downstream. The source collection's reference must not simply
fill an unknown analysis reference; the connecting preparation record matters.

```{r terrain-recorded-metadata, results='asis'}
if (!is.null(tr$recorded_metadata) && nrow(tr$recorded_metadata)) {
  cat('<h4>Previously recorded artifact metadata</h4><p>These are supplied manifest assertions, not newly observed file declarations or a project-wide analysis choice.</p>')
  recorded <- tr$recorded_metadata
  tab(data.frame(Artifact=tr$files$label[match(recorded$artifact_id,tr$files$artifact_id)],
    'Recorded vertical reference'=ifelse(is.na(recorded$vertical_reference),'Not recorded',recorded$vertical_reference),
    'Recorded elevation unit'=ifelse(is.na(recorded$vertical_unit),'Not recorded',recorded$vertical_unit),
    Evidence=ifelse(is.na(recorded$metadata_evidence),'Not recorded',recorded$metadata_evidence),check.names=FALSE))
}
```

### Terrain references: what to do next

```{r terrain-next, results='asis'}
actions <- data.frame(Question=character(),Next=character())
if (any(a$basis=='UNRESOLVED')) actions <- rbind(actions,data.frame(
  Question='Which analysis reference was chosen?',
  Next='Recover or define the unresolved project choices, retaining attributed evidence and exceptions.'))
if (any(a$basis %in% c('OWNER_RECOLLECTION','PROPOSED'))) actions <- rbind(actions,data.frame(
  Question='How strong is the recorded choice?',
  Next='Keep recollections and proposals distinct from a supported project record; obtain corroboration where needed.'))
dems <- f[f$role=='ANALYSIS_DEM',,drop=FALSE]
if (!nrow(dems) || anyNA(dems$preparation_note)) actions <- rbind(actions,data.frame(
  Question='How did the source become the analysis DEM?',
  Next='Locate the source edition and preparation recipe: reference changes, unit conversion, grid and conditioning. Do not infer a link from dates or names.'))
if (nrow(f)) {
  groups <- split(seq_len(nrow(f)), f$next_action)
  for (g in groups) actions <- rbind(actions,data.frame(
    Question=paste(f$label[g],collapse='; '),Next=f$next_action[g[1]]))
  noted <- which(!is.na(f$review_note))
  for (g in split(noted,f$review_note[noted])) actions <- rbind(actions,data.frame(
    Question=paste(f$label[g],collapse='; '),Next=paste('Supplied review note:',f$review_note[g[1]])))
}
if (nrow(actions)) {
  tab(actions)
} else cat('<p>No file or analysis-choice questions were generated for this supplied snapshot; this is not scientific acceptance.</p>')
```

Unit conversion, vertical-datum transformation and resampling are different
operations. Missing preparation records do not demonstrate mishandling by the
original analyst. Evidence can be added later without relabeling the archive.

<details>
<summary>Supporting terrain record: evidence, preparation notes and reader definitions</summary>

```{r terrain-details, results='asis'}
cat('<p>Observation snapshot: ',esc(tr$generated_at),'. Rendering does not reopen files.</p>')
if (!is.null(tr$context_links) && nrow(tr$context_links)) {
  cat('<h4>Explicit saved event selections</h4>')
  tab(tr$context_links)
}
tab(data.frame(Component=unname(component[a$component]),
  Evidence=ifelse(is.na(a$evidence),'Not yet recorded',a$evidence)))
for (i in seq_len(nrow(f))) {
  cat('<h4>',esc(f$label[i]),'</h4>')
  tab(data.frame(Item=c('Local artifact ID','Supplied role/selection evidence',
    'Inspection outcome','Reader comparison','Exposed band unit','Review note','Review evidence',
    'Preparation account (supplied, not independently verified)','Preparation evidence'),
    Record=c(f$artifact_id[i],f$evidence[i],f$inspection_status[i],f$reader_note[i],f$band_unit[i],
      ifelse(is.na(f$review_note[i]),'None supplied',f$review_note[i]),
      ifelse(is.na(f$review_evidence[i]),'None supplied',f$review_evidence[i]),
      ifelse(is.na(f$preparation_note[i]),'Not yet recovered',f$preparation_note[i]),
      ifelse(is.na(f$preparation_evidence[i]),'Not yet recovered',f$preparation_evidence[i]))))
  o <- tr$observations[[f$artifact_id[i]]]
  if (!is.null(o) && is.null(o$error)) {
    cat('<p>File SHA-256: <code>',esc(o$sha256),'</code></p>')
    tab(data.frame(Software=names(unlist(o$software)),Version=as.character(unlist(o$software))))
    for (view in c('default_reader','internal_compound')) {
      v <- o[[view]]
      cat('<details><summary>',if (view=='default_reader') 'Ordinary reader definition' else 'Internal compound-CRS definition',
        '</summary><p>',esc(v$status),'</p><pre>',esc(v$wkt),'</pre>')
      cat('<pre>',esc(jsonlite::toJSON(list(open_options=v$open_options,config_options=v$config_options,
        projjson=v$projjson),auto_unbox=TRUE,pretty=TRUE,null='null')),'</pre></details>')
    }
  }
}
```

Differences between reader views may reflect reader options, sidecars or competing
declarations. They are a reason to inspect evidence, not an automatic diagnosis.
Original file paths and raw error messages are retained in the R review object,
but omitted here to avoid exposing local workstation details.

</details>
