---
title: "Terrain Development"
subtitle: "Study structure, terrain evidence and archive reconstruction"
output:
  html_document:
    self_contained: true
    mathjax: null
    toc: true
    toc_depth: 2
params:
  report: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = TRUE)
r <- params$report
esc <- function(x) {
  x <- gsub("&", "&amp;", x, fixed = TRUE)
  x <- gsub("<", "&lt;", x, fixed = TRUE)
  gsub(">", "&gt;", x, fixed = TRUE)
}
table_html <- function(x, fields = names(x)) {
  if (is.null(x) || !nrow(x)) return(cat("<p>Not supplied or no records supplied.</p>\n"))
  x <- as.data.frame(sf::st_drop_geometry(x))
  cat('<div class="table-responsive">', as.character(knitr::kable(x[intersect(fields, names(x))], format = "html", escape = TRUE, row.names = FALSE)), '</div>')
}
paragraphs_html <- function(x) {
  if (is.null(x) || is.na(x)) return(invisible(NULL))
  paragraphs <- strsplit(x, "\n[[:space:]]*\n", perl = TRUE)[[1]]
  cat(paste0('<p>', esc(paragraphs), '</p>', collapse = '\n'))
}
geographic_hierarchy <- configuration_hierarchy <- r$hierarchy
if (!is.null(r$hierarchy)) {
  geographic_hierarchy <- r$hierarchy[r$hierarchy$entity_type %in%
    c('Study Area', 'Stream', 'Reach', 'Survey Event'), , drop = FALSE]
  configuration_hierarchy <- r$hierarchy[r$hierarchy$entity_type %in%
    c('Study Area', 'Configuration', 'Observation'), , drop = FALSE]
  if (!any(configuration_hierarchy$entity_type %in% c('Configuration', 'Observation')))
    configuration_hierarchy <- configuration_hierarchy[FALSE, , drop = FALSE]
}
draw_hierarchy <- function(h) {
  h$y <- rev(seq_len(nrow(h)))
  h$text <- vapply(paste(h$entity_type, h$label, sep = ': '),
    function(x) paste(strwrap(x, width = 27), collapse = '\n'), character(1))
  edges <- h[!is.na(h$parent_key) & h$parent_key %in% h$node_key, , drop = FALSE]
  parents <- match(edges$parent_key, h$node_key)
  edges$x0 <- h$depth[parents]; edges$y0 <- h$y[parents]
  ggplot2::ggplot(h, ggplot2::aes(x = depth, y = y)) +
    ggplot2::geom_segment(data = edges, ggplot2::aes(x = x0, y = y0, xend = depth, yend = y), colour = '#aab8bf') +
    ggplot2::geom_point(ggplot2::aes(colour = entity_type), size = 3, show.legend = FALSE) +
    ggplot2::geom_label(ggplot2::aes(label = text), hjust = 0, nudge_x = 0.07, size = 3.4, linewidth = 0.15, fill = 'white') +
    ggplot2::scale_x_continuous(limits = c(-0.1, max(h$depth) + 1.2)) +
    ggplot2::scale_y_continuous(expand = ggplot2::expansion(add = 0.8)) +
    ggplot2::theme_void()
}
```

<style>
.terrain-detail { border-top: 1px solid #d8e1e5; padding: 0.8em 0; }
.terrain-detail > summary { cursor: pointer; font-weight: 600; color: #254c59; }
.terrain-review { border-left: 4px solid #527b85; padding: 0.2em 1em; background: #f4f8f9; margin: 1em 0; }
.terrain-controls { margin: 1em 0; }
.terrain-controls button { margin-right: 0.5em; padding: 0.4em 0.8em; }
@media print { .terrain-controls { display: none; } }
</style>

## Study scope

This snapshot describes the supplied study and the work still to review.
It does not approve the data or certify readiness for analysis or FGDB loading.

```{r scope, results='asis'}
cat('<h3>What is known about the supplied scope</h3>')
scope <- data.frame(Item = c('Study Area', 'Selected Streams', 'Defined Reaches',
  'Survey Events', 'Study Area boundary'),
  `Supplied information` = c(
    if (is.null(r$study_area)) 'Not supplied' else r$study_area$study_area_name,
    if (is.null(r$streams)) 'Not supplied' else as.character(nrow(r$streams)),
    if (is.null(r$reaches)) 'Not supplied' else as.character(nrow(r$reaches)),
    if (!nrow(r$surveys)) 'None supplied' else paste0(nrow(r$surveys), ' events: ', paste(r$surveys$date_label, collapse = ', ')),
    if (inherits(r$study_area, 'sf')) 'Analyst-supplied AOI' else 'Not supplied; no boundary inferred'),
  check.names = FALSE)
table_html(scope)
if (!is.na(r$analyst_notes)) {
  cat('<h3>Scope notes and qualifications</h3>')
  paragraphs_html(r$analyst_notes)
}
cat("<p><small>Snapshot generated ", esc(format(r$generated_at, tz = "UTC", usetz = TRUE)), ".</small></p>", sep = "")
```

## Review focus

### What is known from the current checks

```{r review-focus, results='asis'}
cat('<div class="terrain-review">')
if (!is.null(r$staging_inventory)) {
  g <- r$staging_inventory$geodatabases
  cat('<p><strong>Legacy staging:</strong> ', nrow(g), ' geodatabase directories found; ',
    sum(g$listing_status != 'UNREADABLE'), ' vector/table layer listings obtained. ',
    'These are source containers, not confirmed Survey Events. Raster content and conversion readiness are not assessed.</p>', sep = '')
}
if (!is.null(r$folder_inventory)) {
  a <- r$folder_inventory$artifacts
  cat('<p><strong>Selected files:</strong> ', sum(a$available), ' of ', nrow(a),
    ' present; ', sum(a$hash_verified), ' match their saved snapshot. ',
    'Matching bytes do not resolve metadata or scientific questions.</p>', sep = '')
} else cat('<p><strong>Selected files:</strong> no intake inspection supplied.</p>')
if (nrow(r$observation)) {
  cat('<p><strong>Network review:</strong> ', esc(r$observation$review_status),
    if (!is.null(r$validation)) paste0('; current checks: ', esc(r$validation$stream_network_validation_run$result)) else '',
    '. Network status does not establish terrain readiness.</p>', sep = '')
} else cat('<p><strong>Network review:</strong> no network supplied.</p>')
cat('</div>')
```

### What to do next

Blocking checks appear first, followed by analyst input and then further
assessment. This is a review order, **not a prescribed processing sequence**;
rows within each category have no assigned priority. Repeated prompts are shown
once with the number of affected records, not a request to make one decision for all.

```{r next-actions, results='asis'}
actions <- r$review_actions
if (is.null(actions)) {
  cat('<p>Grouped review is unavailable in this older snapshot; consult the detailed findings.</p>')
} else if (!nrow(actions)) {
  cat('<p>No pending prompts in the supplied assessment. This is not a completeness or readiness verdict.</p>')
} else {
  work <- ifelse(actions$status == 'BLOCKED', 'Resolve blocking check',
    ifelse(actions$requires_input, 'Analyst input', 'Further assessment'))
  units <- c(FILE_INTEGRITY = 'file(s)', TERRAIN_REVIEW = 'event(s)',
    STUDY_DEFINITION = 'Study Area reference(s)', HIERARCHY_RECONSTRUCTION = 'archive case(s)',
    EVENT_ASSOCIATION = 'event reference(s)', LEGACY_STAGING = 'staging location(s)')
  affected <- unname(units[actions$stage]); affected[is.na(affected)] <- 'record(s)'
  display <- data.frame(Work = work, `Applies to` = paste(actions$entity_count, affected),
    `Next action` = actions$next_action, check.names = FALSE)
  table_html(display)
}
```

This is a limited review queue, not an exhaustive task list. Network findings,
context qualifications and supplied decisions remain in the supporting record.
“Further assessment” is unfinished work, not necessarily a question for the analyst
or a check that the software can already perform automatically.

## Study structure

### Geographic hierarchy

The Study Area contains selected Streams, their Reaches and the Survey Events
associated with each Reach. These are supplied relationships, not boundaries
or identities inferred from names or spatial overlap.

```{r structure, fig.width=10, fig.height=max(4, 0.55 * nrow(geographic_hierarchy)), fig.alt="Geographic hierarchy: Study Area, Streams, Reaches and Survey Events.", fig.cap="Geographic study organization and its Survey Events. Configuration records are shown separately below."}
if (!is.null(geographic_hierarchy) && nrow(geographic_hierarchy)) {
  print(draw_hierarchy(geographic_hierarchy))
} else cat("No hierarchy supplied. Archive interpretations can be recorded without assigning identities.")
```

### Network configuration records

A Configuration organizes network records for the Study Area; an Observation
records a network state. These records do not sit inside the Reach hierarchy.
The repeated Study Area is an ownership reference, not a second Study Area.
An Observation is not a Survey Event, even if their years match.

```{r configuration-structure, fig.width=10, fig.height=max(3, 0.65 * nrow(configuration_hierarchy)), fig.alt="Network record relationships: Study Area ownership, Configuration and Observation.", fig.cap="Configuration and Observation records, with Study Area ownership shown for context."}
if (!is.null(configuration_hierarchy) && nrow(configuration_hierarchy)) {
  print(draw_hierarchy(configuration_hierarchy))
} else cat("No network Configuration or Observation records supplied.")
```

## Spatial overview

```{r overview, fig.width=9, fig.height=6}
layers <- Filter(Negate(is.null), list(r$segments,
  if (inherits(r$study_area, "sf")) r$study_area else NULL, r$dem_extent,
  if (inherits(r$streams, "sf")) r$streams else NULL,
  if (inherits(r$reaches, "sf")) r$reaches else NULL))
if (length(layers)) {
  crs <- sf::st_crs(layers[[1]])
  p <- ggplot2::ggplot()
  if (!is.null(r$dem_extent)) p <- p + ggplot2::geom_sf(data = r$dem_extent, fill = "#e8eef3", colour = "#70869a", linetype = "dashed")
  if (inherits(r$study_area, "sf")) p <- p + ggplot2::geom_sf(data = r$study_area, fill = NA, colour = "#1d3038", linewidth = 1)
  if (inherits(r$streams, "sf")) p <- p + ggplot2::geom_sf(data = r$streams, fill = NA, colour = "#5e8d7b", linetype = "dotted")
  if (inherits(r$reaches, "sf")) p <- p + ggplot2::geom_sf(data = r$reaches, fill = NA, colour = "#a36945", linetype = "dotdash")
  if (!is.null(r$segments)) p <- p + ggplot2::geom_sf(data = r$segments, ggplot2::aes(colour = report_reach), linewidth = 1)
  print(p + ggplot2::coord_sf(crs = crs, datum = crs) + ggplot2::theme_minimal(base_size = 12) +
    ggplot2::scale_x_continuous(n.breaks = 3, labels = scales::label_number(big.mark = ",")) +
    ggplot2::scale_y_continuous(n.breaks = 4, labels = scales::label_number(big.mark = ",")) +
    ggplot2::theme(legend.position = "bottom", axis.text.x = ggplot2::element_text(angle = 45, hjust = 1)) +
    ggplot2::labs(colour = "Network Reach assignment", x = NULL, y = NULL,
      caption = paste("Display CRS:", crs$Name, "| Coordinate units:", crs$units_gdal)))
} else cat("No Study Area, network, or DEM extent supplied for mapping.")
```

Solid dark outline: Study Area AOI. Pale fill and dashed outline: DEM rectangle,
**not its valid-cell footprint**. Optional green dotted and brown dot-dashed
outlines: supplied Stream and Reach AOIs. Network colours show supplied Reach
assignments, not inferred segmentation. No online basemap is requested.

## Evidence across Reaches and time

Each column represents a supplied Survey Event, not every year a study was
expected to cover. Blank cells mean **no event supplied for that Reach and
column**, not a missing required survey. Same-date events remain separate.
"Grid supplied" means a raster object and its grid metadata were supplied for
that event; it does not certify readable cell values, complete coverage,
vertical references or comparable methods.

```{r event-matrix, fig.width=10, fig.height=max(2, 0.5 * length(unique(r$event_evidence$reach_id))), fig.cap="Supplied event evidence, not a readiness or completeness score."}
if (!is.null(r$event_evidence) && nrow(r$event_evidence)) {
  e <- r$event_evidence
  reach_ids <- unique(e$reach_id)
  e$x <- seq_len(nrow(e)); e$y <- match(e$reach_id, rev(reach_ids))
  e$label <- ifelse(e$evidence_status == "GRID_SUPPLIED", "Grid\nsupplied", "Inventory\nonly")
  print(ggplot2::ggplot(e, ggplot2::aes(x = x, y = y)) +
    ggplot2::geom_tile(ggplot2::aes(fill = evidence_status), colour = "white", width = 0.9, height = 0.8) +
    ggplot2::geom_text(ggplot2::aes(label = label), size = 3.5) +
    ggplot2::scale_fill_manual(values = c(GRID_SUPPLIED = "#b7d9d0", INVENTORY_ONLY = "#e4e9ed"), guide = "none") +
    ggplot2::scale_x_continuous(breaks = e$x, labels = paste(e$date_label, paste0("Event ", e$x), sep = "\n")) +
    ggplot2::scale_y_continuous(breaks = seq_along(reach_ids),
      labels = e$reach_label[match(rev(reach_ids), e$reach_id)]) +
    ggplot2::theme_minimal(base_size = 12) + ggplot2::labs(x = NULL, y = NULL))
} else cat("Survey Events have not been supplied; no expected time sequence is assumed.")
```

### Survey terrain extents

```{r event-extents, fig.width=10, fig.height=6, fig.cap="Supplied DEM grid rectangles by event. These are not valid-cell footprints or Study Area boundaries."}
if (!is.null(r$survey_dem_extents)) {
  p <- ggplot2::ggplot(r$survey_dem_extents) +
    ggplot2::geom_sf(fill = "#e8eef3", colour = "#70869a", linetype = "dashed")
  if (inherits(r$study_area, "sf")) p <- p + ggplot2::geom_sf(data = r$study_area, fill = NA, colour = "#1d3038")
  display_crs <- sf::st_crs(r$survey_dem_extents)
  print(p + ggplot2::facet_wrap(~panel, labeller = ggplot2::label_wrap_gen(width = 22)) +
    ggplot2::coord_sf(crs = display_crs, datum = display_crs) + ggplot2::theme_minimal(base_size = 10) +
    ggplot2::scale_x_continuous(n.breaks = 2, labels = scales::label_number(big.mark = ",")) +
    ggplot2::scale_y_continuous(n.breaks = 3, labels = scales::label_number(big.mark = ",")) +
    ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1)) +
    ggplot2::labs(caption = paste("Common display CRS:", display_crs$Name, "| Units:", display_crs$units_gdal)))
} else cat("No event-associated DEM grids supplied.")
```

## Supporting record

The sections below retain the detailed evidence for another analyst or customer.
Expand them as needed; expanding a section does not change any data or decisions.
Printing this HTML expands the record automatically when JavaScript is enabled.

<div class="terrain-controls">
<button type="button" onclick="terrainDetails(true)">Expand supporting record</button>
<button type="button" onclick="terrainDetails(false)">Collapse supporting record</button>
</div>

<details class="terrain-detail">
<summary>Survey terrain grid metadata</summary>

```{r event-evidence, results='asis'}
table_html(r$event_evidence, c("reach_label", "date_label", "evidence_status", "source_dataset",
  "rows", "columns", "x_cell_size", "y_cell_size", "horizontal_units", "horizontal_crs"))
```

</details>

<details class="terrain-detail">
<summary>Legacy project reconstruction and portable intake files</summary>

```{r legacy-staging, results='asis'}
if (!is.null(r$staging_inventory)) {
  cat('<h3>FileGDB staging inventory</h3><p>Read-only comparison with staging draft 0.1. Locations are not governed identities. Layer metadata does not verify feature values, clean source selection, rasters, acquisition dates or archive-to-copy equality.</p>')
  table_html(r$staging_inventory$geodatabases)
  cat('<h4>Expected catalog records</h4><p>Presence only: fields, values, parentage and boundary validity are not checked. Missing records refer to the draft profile, not a previously imposed archive requirement.</p>')
  catalogs <- r$staging_inventory$catalogs
  catalogs$present <- ifelse(is.na(catalogs$present), 'Unknown: location not inspected or container unreadable',
    ifelse(catalogs$present, 'Present; values not validated', 'Not found'))
  table_html(catalogs)
  cat('<details><summary>Driver-reported vector and table layers</summary><p>Unknown feature counts are not zero. Geometry types include driver-reported Z/M dimensions; this listing does not test their values. Rasters are outside this inventory.</p>')
  table_html(r$staging_inventory$layers)
  cat('</details>')
}
```

<h3>Portable intake files</h3>

The optional inventory below checks selected files against their saved snapshot.
It is not a complete event manifest, proof of archive conversion, or FGDB acceptance.
Local intake/artifact labels do not assign Study Area or Survey Event identities.
Matching bytes do not establish vertical meaning or adequate terrain coverage.

```{r intake-inventory, results='asis'}
if (!is.null(r$folder_inventory)) {
  cat("<p>Intake case: ", esc(r$folder_inventory$intake_id), "</p>", sep = "")
  inventory <- r$folder_inventory$artifacts
  inventory$available <- ifelse(inventory$available, "Present", "Missing")
  inventory$hash_verified <- ifelse(inventory$hash_verified, "Matches snapshot", "Not verified")
  for (field in c("vertical_reference", "vertical_unit")) inventory[[field]][is.na(inventory[[field]])] <- "Unknown"
  names(inventory) <- c("Artifact", "Role / source label", "Relative path", "Format",
    "File", "Snapshot integrity", "Vertical reference", "Elevation units")
  cat('<div class="table-responsive">')
  table_html(inventory)
  cat('</div>')
} else cat("<p>No portable intake manifest supplied.</p>")
```

<h3>Archive interpretations</h3>

Surviving artifacts may support several interpretations of the original study.
The entries below keep source evidence, proposed structure and supplied analyst
decisions separate. **CONFIRMED** records the analyst's interpretation, not
independent verification, governed identity reconciliation or approval to load
FGDB. Rejected interpretations remain visible. Nothing in this ledger creates
or changes the hierarchy above.

```{r reconstruction, results='asis'}
table_html(r$reconstruction)
```

</details>

<details class="terrain-detail">
<summary>All assessment findings and affected records</summary>

Each source finding is retained, including successful checks and supplied
decisions. Review references are local bookkeeping identifiers, not priorities
or persistent task IDs.

```{r actions, results='asis'}
if (!is.null(r$assessment)) {
  findings <- r$assessment
  findings$review_reference <- rep(NA_integer_, nrow(findings))
  if (!is.null(r$review_action_members)) {
    m <- r$review_action_members
    findings$review_reference[m$assessment_row] <- m$action_id
  }
  table_html(findings, c("review_reference", "entity_label", "stage", "status", "requires_input", "next_action"))
}
cat("<h4>Additional context and network qualifications</h4>")
cat("<ul>", paste0("<li>", esc(r$gaps), "</li>", collapse = ""), "</ul></details>")
```

<details class="terrain-detail">
<summary>Streams, Reaches and Survey Event inventory</summary>

<h3>Selected Streams</h3>

```{r streams, results='asis'}
table_html(r$streams, "stream_name")
```

<h3>Reach definitions</h3>

```{r reaches, results='asis'}
table_html(r$reaches, c("stream_name", "reach_name"))
```

<h3>Survey Event inventory</h3>

Dates retain their supplied precision. Inventory does not establish which files
remain available, a base event, or a relationship to this network observation.

```{r surveys, results='asis'}
table_html(r$surveys, c("reach_name", "date_label", "source_dataset", "availability_notes"))
```

```{r event-artifacts, results='asis'}
if (!is.null(r$event_artifacts) && nrow(r$event_artifacts)) {
  cat('<h3>Terrain file associations</h3><p>These are supplied associations, not independent confirmation of provenance or FGDB identities. Only explicitly selected, unblocked DEMs supply event grid views.</p>')
  links <- r$event_artifacts
  idx <- match(links$survey_event_id, r$surveys$survey_event_id)
  links$reach <- r$surveys$reach_name[idx]
  links$event <- r$surveys$date_label[idx]
  links$reach[is.na(idx)] <- 'Context not supplied'
  links$event[is.na(idx)] <- 'Unresolved event reference'
  labels <- c(GRID_LOADED = 'Grid loaded; not scientifically assessed',
    NOT_LOADED = 'Selected; grid not loaded', NOT_SELECTED = 'Retained; not selected for grid view')
  table_html(data.frame(Reach = links$reach, Event = links$event, Purpose = links$purpose,
    File = links$path, `Report use` = unname(labels[links$grid_status]), check.names = FALSE))
  cat('<details><summary>Association evidence and identity references</summary>')
  table_html(links, c('artifact_id', 'survey_event_id', 'evidence', 'analyst', 'use_for_report'))
  cat('</details>')
}
```

</details>

<details class="terrain-detail">
<summary>Terrain and network provenance</summary>

```{r terrain, results='asis'}
if (!is.na(r$terrain_notes)) cat("<p>", esc(r$terrain_notes), "</p>", sep = "")
table_html(r$terrain)
if (nrow(r$observation)) {
  fields <- intersect(c("evidence_class", "coverage_status", "provenance_completeness", "review_status",
    "derivation_method_id", "method_version", "source_terrain_label", "vertical_unit", "native_vertical_datum"), names(r$observation))
  table_html(data.frame(property = fields, value = vapply(r$observation[fields], as.character, character(1))))
}
```

The supplied DEM is not asserted to be the original derivation surface. This
first report shows its extent and grid metadata; it does not assess internal
NoData, elevation quality, hydro-conditioning or Level 1 input completeness.
Network acceptance and local technical validation are separate facts.

</details>

<details class="terrain-detail">
<summary>Network checks and identity references</summary>

```{r checks, results='asis'}
if (!is.null(r$validation)) {
  table_html(r$validation$stream_network_validation_run, c("validation_level", "result", "validated_at"))
  findings <- r$validation$stream_network_validation_issue
  if (nrow(findings)) table_html(findings, c("issue_code", "message"))
}
cat("<details><summary>Identity references</summary>")
table_html(r$study_area, c("study_area_name", "study_area_id"))
table_html(r$streams, c("stream_name", "stream_id", "study_area_id"))
table_html(r$reaches, c("reach_name", "reach_id", "stream_id"))
table_html(r$surveys, c("date_label", "survey_event_id", "reach_id"))
table_html(r$assessment, c("code", "entity_label", "entity_id"))
cat("</details>")
```

The report does not change source data, stored validation history, review
decisions, or acceptance status. Detailed network lineage and operation evidence
remain in the accompanying relation bundle/GeoPackage.

</details>

<script>
function terrainDetails(open) {
  document.querySelectorAll('details.terrain-detail, details.terrain-detail details').forEach(function(item) { item.open = open; });
}
var terrainPrintState = null;
window.addEventListener('beforeprint', function() {
  if (terrainPrintState !== null) return;
  terrainPrintState = Array.from(document.querySelectorAll('details.terrain-detail, details.terrain-detail details')).map(function(item) {
    return { item: item, open: item.open };
  });
  terrainDetails(true);
});
window.addEventListener('afterprint', function() {
  if (terrainPrintState !== null) terrainPrintState.forEach(function(state) { state.item.open = state.open; });
  terrainPrintState = null;
});
</script>
