---
title: "Terrain clipping: completed operation"
output:
  html_document:
    self_contained: true
    toc: false
params:
  report: null
  terrain: null
  aoi: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
r <- params$report
```

```{r styling, results='asis'}
cat(knitr::raw_html(paste0('<style>', report_table_css, '</style>')))
```

## What happened

The tool cropped a DEM to the supplied AOI bounds and masked cells outside the
chosen polygon coverage. It preserved the source grid and retained elevations;
it did not resample, convert units, transform a datum, fill gaps or condition a
channel. Existing NoData stayed masked. NoData is not a quality percentage.

```{r overview, results='asis'}
report_table(data.frame(
  Item = c(
    'Source DEM',
    'New DEM',
    'Why this AOI was selected',
    'Boundary-cell rule',
    'Source / output rows and columns',
    'Cell size (CRS units)',
    'Elevation-band unit',
    'Outcome'
  ),
  Detail = c(
    r$input$filename,
    r$output$path,
    r$rationale,
    if (r$parameters$touches) {
      'Retain cells touched by the AOI'
    } else {
      'Retain cells whose centers are inside the AOI'
    },
    paste(
      paste(unlist(r$input$grid$dimensions), collapse = ' x '),
      paste(unlist(r$output$grid$dimensions), collapse = ' x '),
      sep = ' / '
    ),
    paste(unlist(r$output$grid$resolution), collapse = ' x '),
    if (nzchar(r$output$reference$band_unit)) {
      r$output$reference$band_unit
    } else {
      'Not declared; no unit was inferred'
    },
    'Completed; local output fingerprints checked when this report was made'
  )
))
```

## Review the result

The red outline is the supplied AOI. Edge cells follow the selected boundary
rule; the output rectangle is aligned to the original raster grid.

```{r map, fig.width=9, fig.height=6, out.width='100%'}
dem <- terra::rast(params$terrain)
aoi <- sf::st_read(params$aoi, layer = 'aoi', quiet = TRUE)
terra::plot(dem, main = 'Clipped terrain and explicit AOI')
plot(sf::st_geometry(aoi), add = TRUE, border = '#c62828', lwd = 2)
```

## What to do next

Confirm that the chosen AOI and boundary-cell rule match the intended analysis.
Keep `terrain.tif`, `aoi.gpkg`, `terrain-manifest.json` and the execution receipts
together. Use the returned terrain in the appropriate Study Area / Survey Event
workflow; this operation does not assign or replace an event's DEM automatically.
**No CSV history entry is needed for this run.**

Clipping does not establish source-collection lineage, recover unknown vertical
metadata or prove that multiple surveys can be compared. The retained source hash
identifies the local input used, not an original lidar collection. The original
source is not copied into this folder or rechecked by this report.

<details>
<summary>Automatic execution record and scope</summary>

```{r execution, results='asis'}
report_table(data.frame(
  Item = c(
    'Operation',
    'Started (UTC)',
    'Completed (UTC)',
    'Bounds / output storage',
    'Source SHA-256',
    'AOI SHA-256',
    'Output SHA-256',
    'Software'
  ),
  Detail = c(
    r$operation,
    r$started_at,
    r$completed_at,
    'Bounds snap out; Float64 GeoTIFF; DEFLATE compression',
    r$input$sha256,
    r$aoi$sha256,
    r$output$sha256,
    paste(
      'fluvgeo',
      r$software$fluvgeo,
      '/ terra',
      r$software$terra,
      '/ R',
      r$software$R
    )
  )
))
```

`execution.json` stores the actual settings, software versions, reference/grid
observations and successful checks. `started.json` preserves the start record.
This tool-generated record is separate from attributed accounts of past work;
it is not a signed certificate or a general-purpose executable recipe.

This first implementation supports self-contained, single-band projected 2D
GeoTIFFs and same-CRS polygon AOIs. It refuses auxiliary-file dependencies,
compound/3D reference systems, rotated grids and categorical rasters. Those
boundaries require separate qualification; known references must never be dropped
to make a file pass.

</details>
