---
title: "Terrain Development"
subtitle: "Study definition and pre-Level-1 review"
output:
  html_document:
    self_contained: true
    mathjax: null
    toc: true
    toc_depth: 2
params:
  report: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = TRUE)
r <- params$report
esc <- function(x) {
  x <- gsub("&", "&amp;", x, fixed = TRUE)
  x <- gsub("<", "&lt;", x, fixed = TRUE)
  gsub(">", "&gt;", x, fixed = TRUE)
}
table_html <- function(x, fields = names(x)) {
  if (is.null(x) || !nrow(x)) return(cat("<p>Not supplied or no records supplied.</p>\n"))
  x <- as.data.frame(sf::st_drop_geometry(x))
  cat(as.character(knitr::kable(x[intersect(fields, names(x))], format = "html", escape = TRUE, row.names = FALSE)))
}
```

## Study scope

This is a read-only review of supplied local inputs, not a Level 1 readiness
certificate. Missing information is shown below; no Survey Events, boundaries,
or review decisions have been inferred. The AOI is an analyst-defined study
extent, not an official boundary or a watershed derived from this report.

```{r scope, results='asis'}
table_html(r$study_area, "study_area_name")
cat("<p>Generated ", esc(format(r$generated_at, tz = "UTC", usetz = TRUE)), ".</p>", sep = "")
if (!is.na(r$analyst_notes)) cat("<p>", esc(r$analyst_notes), "</p>", sep = "")
cat("<p>", if (is.null(r$streams)) "Unknown" else nrow(r$streams), " selected Streams; ",
    if (is.null(r$reaches)) "unknown" else nrow(r$reaches), " defined Reaches; ",
    nrow(r$surveys), " supplied Survey Events.</p>", sep = "")
```

## Decisions and missing evidence

```{r gaps, results='asis'}
cat("<ul>", paste0("<li>", esc(r$gaps), "</li>", collapse = ""), "</ul>")
```

## Spatial overview

```{r overview, fig.width=9, fig.height=6}
layers <- Filter(Negate(is.null), list(r$segments, r$study_area, r$dem_extent,
  if (inherits(r$streams, "sf")) r$streams else NULL,
  if (inherits(r$reaches, "sf")) r$reaches else NULL))
if (length(layers)) {
  crs <- sf::st_crs(layers[[1]])
  p <- ggplot2::ggplot()
  if (!is.null(r$dem_extent)) p <- p + ggplot2::geom_sf(data = r$dem_extent, fill = "#e8eef3", colour = "#70869a", linetype = "dashed")
  if (!is.null(r$study_area)) p <- p + ggplot2::geom_sf(data = r$study_area, fill = NA, colour = "#1d3038", linewidth = 1)
  if (inherits(r$streams, "sf")) p <- p + ggplot2::geom_sf(data = r$streams, fill = NA, colour = "#5e8d7b", linetype = "dotted")
  if (inherits(r$reaches, "sf")) p <- p + ggplot2::geom_sf(data = r$reaches, fill = NA, colour = "#a36945", linetype = "dotdash")
  if (!is.null(r$segments)) p <- p + ggplot2::geom_sf(data = r$segments, ggplot2::aes(colour = report_reach), linewidth = 1)
  print(p + ggplot2::coord_sf(crs = crs, datum = crs) + ggplot2::theme_minimal(base_size = 12) +
    ggplot2::scale_x_continuous(n.breaks = 3, labels = scales::label_number(big.mark = ",")) +
    ggplot2::scale_y_continuous(n.breaks = 4, labels = scales::label_number(big.mark = ",")) +
    ggplot2::theme(legend.position = "bottom", axis.text.x = ggplot2::element_text(angle = 45, hjust = 1)) +
    ggplot2::labs(colour = "Network Reach assignment", x = NULL, y = NULL,
      caption = paste("Display CRS:", crs$Name, "| Coordinate units:", crs$units_gdal)))
} else cat("No Study Area, network, or DEM extent supplied for mapping.")
```

Solid dark outline: Study Area AOI. Pale fill and dashed outline: DEM rectangle,
**not its valid-cell footprint**. Optional green dotted and brown dot-dashed
outlines: supplied Stream and Reach AOIs. Network colours show supplied Reach
assignments, not inferred segmentation. No online basemap is requested.

## Streams, Reaches and Survey Events

### Selected Streams

```{r streams, results='asis'}
table_html(r$streams, "stream_name")
```

### Reach definitions

```{r reaches, results='asis'}
table_html(r$reaches, c("stream_name", "reach_name"))
```

### Survey Event inventory

Dates retain their supplied precision. Inventory does not establish which files
remain available, a base event, or a relationship to this network observation.

```{r surveys, results='asis'}
table_html(r$surveys, c("reach_name", "date_label", "source_dataset", "availability_notes"))
```

## Terrain and network evidence

```{r terrain, results='asis'}
if (!is.na(r$terrain_notes)) cat("<p>", esc(r$terrain_notes), "</p>", sep = "")
table_html(r$terrain)
if (nrow(r$observation)) {
  fields <- intersect(c("evidence_class", "coverage_status", "provenance_completeness", "review_status",
    "derivation_method_id", "method_version", "source_terrain_label", "vertical_unit", "native_vertical_datum"), names(r$observation))
  table_html(data.frame(property = fields, value = vapply(r$observation[fields], as.character, character(1))))
}
```

The supplied DEM is not asserted to be the original derivation surface. This
first report shows its extent and grid metadata; it does not assess internal
NoData, elevation quality, hydro-conditioning or Level 1 input completeness.
Network acceptance and local technical validation are separate facts.

## Network checks and identity references

```{r checks, results='asis'}
if (!is.null(r$validation)) {
  table_html(r$validation$stream_network_validation_run, c("validation_level", "result", "validated_at"))
  findings <- r$validation$stream_network_validation_issue
  if (nrow(findings)) table_html(findings, c("issue_code", "message"))
}
cat("<details><summary>Identity references</summary>")
table_html(r$study_area, c("study_area_name", "study_area_id"))
table_html(r$streams, c("stream_name", "stream_id", "study_area_id"))
table_html(r$reaches, c("reach_name", "reach_id", "stream_id"))
table_html(r$surveys, c("date_label", "survey_event_id", "reach_id"))
cat("</details>")
```

The report does not change source data, stored validation history, review
decisions, or acceptance status. Detailed network lineage and operation evidence
remain in the accompanying relation bundle/GeoPackage.
