---
title: "Terrain Development"
subtitle: "Study structure, terrain evidence and archive reconstruction"
output:
  html_document:
    self_contained: true
    mathjax: null
    toc: true
    toc_depth: 2
params:
  report: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = TRUE)
r <- params$report
esc <- function(x) {
  x <- gsub("&", "&amp;", x, fixed = TRUE)
  x <- gsub("<", "&lt;", x, fixed = TRUE)
  gsub(">", "&gt;", x, fixed = TRUE)
}
table_html <- function(x, fields = names(x)) {
  if (is.null(x) || !nrow(x)) return(cat("<p>Not supplied or no records supplied.</p>\n"))
  x <- as.data.frame(sf::st_drop_geometry(x))
  cat(as.character(knitr::kable(x[intersect(fields, names(x))], format = "html", escape = TRUE, row.names = FALSE)))
}
```

## Study scope

This is a read-only review of supplied local inputs, not a Level 1 readiness
certificate. Missing information is shown below; no Survey Events, boundaries,
or review decisions have been inferred. The AOI is an analyst-defined study
extent, not an official boundary or a watershed derived from this report.

```{r scope, results='asis'}
table_html(r$study_area, "study_area_name")
cat("<p>Generated ", esc(format(r$generated_at, tz = "UTC", usetz = TRUE)), ".</p>", sep = "")
if (!is.na(r$analyst_notes)) cat("<p>", esc(r$analyst_notes), "</p>", sep = "")
cat("<p>", if (is.null(r$streams)) "Unknown" else nrow(r$streams), " selected Streams; ",
    if (is.null(r$reaches)) "unknown" else nrow(r$reaches), " defined Reaches; ",
    nrow(r$surveys), " supplied Survey Events.</p>", sep = "")
```

## Study structure

This view describes supplied identities and relationships, not a reconstruction
from names or spatial overlap. Missing context is not filled in automatically.
Network Configurations belong to the Study Area; their Observations are distinct
from Reach Survey Events, even when they share a year.

```{r structure, fig.width=10, fig.height=max(4, 0.55 * nrow(r$hierarchy)), fig.cap="Study organization from supplied relationships. Names and dates are display labels; identity references are retained below."}
if (!is.null(r$hierarchy) && nrow(r$hierarchy)) {
  h <- r$hierarchy
  h$y <- rev(seq_len(nrow(h)))
  h$text <- vapply(paste(h$entity_type, h$label, sep = ": "),
    function(x) paste(strwrap(x, width = 27), collapse = "\n"), character(1))
  edges <- h[!is.na(h$parent_key), , drop = FALSE]
  parents <- match(edges$parent_key, h$node_key)
  edges$x0 <- h$depth[parents]; edges$y0 <- h$y[parents]
  print(ggplot2::ggplot(h, ggplot2::aes(x = depth, y = y)) +
    ggplot2::geom_segment(data = edges, ggplot2::aes(x = x0, y = y0, xend = depth, yend = y), colour = "#aab8bf") +
    ggplot2::geom_point(ggplot2::aes(colour = entity_type), size = 3, show.legend = FALSE) +
    ggplot2::geom_label(ggplot2::aes(label = text), hjust = 0, nudge_x = 0.07, size = 3.4, linewidth = 0.15, fill = "white") +
    ggplot2::scale_x_continuous(limits = c(-0.1, 4.2)) +
    ggplot2::scale_y_continuous(expand = ggplot2::expansion(add = 0.8)) +
    ggplot2::theme_void())
} else cat("No hierarchy supplied. Archive interpretations can be recorded without assigning identities.")
```

## Spatial overview

```{r overview, fig.width=9, fig.height=6}
layers <- Filter(Negate(is.null), list(r$segments,
  if (inherits(r$study_area, "sf")) r$study_area else NULL, r$dem_extent,
  if (inherits(r$streams, "sf")) r$streams else NULL,
  if (inherits(r$reaches, "sf")) r$reaches else NULL))
if (length(layers)) {
  crs <- sf::st_crs(layers[[1]])
  p <- ggplot2::ggplot()
  if (!is.null(r$dem_extent)) p <- p + ggplot2::geom_sf(data = r$dem_extent, fill = "#e8eef3", colour = "#70869a", linetype = "dashed")
  if (inherits(r$study_area, "sf")) p <- p + ggplot2::geom_sf(data = r$study_area, fill = NA, colour = "#1d3038", linewidth = 1)
  if (inherits(r$streams, "sf")) p <- p + ggplot2::geom_sf(data = r$streams, fill = NA, colour = "#5e8d7b", linetype = "dotted")
  if (inherits(r$reaches, "sf")) p <- p + ggplot2::geom_sf(data = r$reaches, fill = NA, colour = "#a36945", linetype = "dotdash")
  if (!is.null(r$segments)) p <- p + ggplot2::geom_sf(data = r$segments, ggplot2::aes(colour = report_reach), linewidth = 1)
  print(p + ggplot2::coord_sf(crs = crs, datum = crs) + ggplot2::theme_minimal(base_size = 12) +
    ggplot2::scale_x_continuous(n.breaks = 3, labels = scales::label_number(big.mark = ",")) +
    ggplot2::scale_y_continuous(n.breaks = 4, labels = scales::label_number(big.mark = ",")) +
    ggplot2::theme(legend.position = "bottom", axis.text.x = ggplot2::element_text(angle = 45, hjust = 1)) +
    ggplot2::labs(colour = "Network Reach assignment", x = NULL, y = NULL,
      caption = paste("Display CRS:", crs$Name, "| Coordinate units:", crs$units_gdal)))
} else cat("No Study Area, network, or DEM extent supplied for mapping.")
```

Solid dark outline: Study Area AOI. Pale fill and dashed outline: DEM rectangle,
**not its valid-cell footprint**. Optional green dotted and brown dot-dashed
outlines: supplied Stream and Reach AOIs. Network colours show supplied Reach
assignments, not inferred segmentation. No online basemap is requested.

## Evidence across Reaches and time

Each column represents a supplied Survey Event, not every year a study was
expected to cover. Blank cells mean **no event supplied for that Reach and
column**, not a missing required survey. Same-date events remain separate.
"Grid supplied" means a raster object and its grid metadata were supplied for
that event; it does not certify readable cell values, complete coverage,
vertical references or comparable methods.

```{r event-matrix, fig.width=10, fig.height=max(2, 0.5 * length(unique(r$event_evidence$reach_id))), fig.cap="Supplied event evidence, not a readiness or completeness score."}
if (!is.null(r$event_evidence) && nrow(r$event_evidence)) {
  e <- r$event_evidence
  reach_ids <- unique(e$reach_id)
  e$x <- seq_len(nrow(e)); e$y <- match(e$reach_id, rev(reach_ids))
  e$label <- ifelse(e$evidence_status == "GRID_SUPPLIED", "Grid\nsupplied", "Inventory\nonly")
  print(ggplot2::ggplot(e, ggplot2::aes(x = x, y = y)) +
    ggplot2::geom_tile(ggplot2::aes(fill = evidence_status), colour = "white", width = 0.9, height = 0.8) +
    ggplot2::geom_text(ggplot2::aes(label = label), size = 3.5) +
    ggplot2::scale_fill_manual(values = c(GRID_SUPPLIED = "#b7d9d0", INVENTORY_ONLY = "#e4e9ed"), guide = "none") +
    ggplot2::scale_x_continuous(breaks = e$x, labels = paste(e$date_label, paste0("Event ", e$x), sep = "\n")) +
    ggplot2::scale_y_continuous(breaks = seq_along(reach_ids),
      labels = e$reach_label[match(rev(reach_ids), e$reach_id)]) +
    ggplot2::theme_minimal(base_size = 12) + ggplot2::labs(x = NULL, y = NULL))
} else cat("Survey Events have not been supplied; no expected time sequence is assumed.")
```

### Survey terrain extents

```{r event-extents, fig.width=10, fig.height=6, fig.cap="Supplied DEM grid rectangles by event. These are not valid-cell footprints or Study Area boundaries."}
if (!is.null(r$survey_dem_extents)) {
  p <- ggplot2::ggplot(r$survey_dem_extents) +
    ggplot2::geom_sf(fill = "#e8eef3", colour = "#70869a", linetype = "dashed")
  if (inherits(r$study_area, "sf")) p <- p + ggplot2::geom_sf(data = r$study_area, fill = NA, colour = "#1d3038")
  display_crs <- sf::st_crs(r$survey_dem_extents)
  print(p + ggplot2::facet_wrap(~panel, labeller = ggplot2::label_wrap_gen(width = 22)) +
    ggplot2::coord_sf(crs = display_crs, datum = display_crs) + ggplot2::theme_minimal(base_size = 10) +
    ggplot2::scale_x_continuous(n.breaks = 2, labels = scales::label_number(big.mark = ",")) +
    ggplot2::scale_y_continuous(n.breaks = 3, labels = scales::label_number(big.mark = ",")) +
    ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1)) +
    ggplot2::labs(caption = paste("Common display CRS:", display_crs$Name, "| Units:", display_crs$units_gdal)))
} else cat("No event-associated DEM grids supplied.")
```

```{r event-evidence, results='asis'}
table_html(r$event_evidence, c("reach_label", "date_label", "evidence_status", "source_dataset",
  "rows", "columns", "x_cell_size", "y_cell_size", "horizontal_units", "horizontal_crs"))
```

## Legacy project reconstruction

Surviving artifacts may support several interpretations of the original study.
The entries below keep source evidence, proposed structure and supplied analyst
decisions separate. **CONFIRMED** records the analyst's interpretation, not
independent verification, governed identity reconciliation or approval to load
FGDB. Rejected interpretations remain visible. Nothing in this ledger creates
or changes the hierarchy above.

```{r reconstruction, results='asis'}
table_html(r$reconstruction)
```

### Decisions and next actions

These stage-specific prompts are reusable by a client such as Shiny. They are
not a complete migration validator or a single FGDB compliance verdict. Technical
checks and detailed evidence remain available even when no human decision is due.

```{r actions, results='asis'}
table_html(r$assessment, c("entity_label", "stage", "status", "requires_input", "next_action"))
cat("<details><summary>Additional context and network qualifications</summary>")
cat("<ul>", paste0("<li>", esc(r$gaps), "</li>", collapse = ""), "</ul></details>")
```

## Streams, Reaches and Survey Events

### Selected Streams

```{r streams, results='asis'}
table_html(r$streams, "stream_name")
```

### Reach definitions

```{r reaches, results='asis'}
table_html(r$reaches, c("stream_name", "reach_name"))
```

### Survey Event inventory

Dates retain their supplied precision. Inventory does not establish which files
remain available, a base event, or a relationship to this network observation.

```{r surveys, results='asis'}
table_html(r$surveys, c("reach_name", "date_label", "source_dataset", "availability_notes"))
```

## Terrain and network evidence

```{r terrain, results='asis'}
if (!is.na(r$terrain_notes)) cat("<p>", esc(r$terrain_notes), "</p>", sep = "")
table_html(r$terrain)
if (nrow(r$observation)) {
  fields <- intersect(c("evidence_class", "coverage_status", "provenance_completeness", "review_status",
    "derivation_method_id", "method_version", "source_terrain_label", "vertical_unit", "native_vertical_datum"), names(r$observation))
  table_html(data.frame(property = fields, value = vapply(r$observation[fields], as.character, character(1))))
}
```

The supplied DEM is not asserted to be the original derivation surface. This
first report shows its extent and grid metadata; it does not assess internal
NoData, elevation quality, hydro-conditioning or Level 1 input completeness.
Network acceptance and local technical validation are separate facts.

## Network checks and identity references

```{r checks, results='asis'}
if (!is.null(r$validation)) {
  table_html(r$validation$stream_network_validation_run, c("validation_level", "result", "validated_at"))
  findings <- r$validation$stream_network_validation_issue
  if (nrow(findings)) table_html(findings, c("issue_code", "message"))
}
cat("<details><summary>Identity references</summary>")
table_html(r$study_area, c("study_area_name", "study_area_id"))
table_html(r$streams, c("stream_name", "stream_id", "study_area_id"))
table_html(r$reaches, c("reach_name", "reach_id", "stream_id"))
table_html(r$surveys, c("date_label", "survey_event_id", "reach_id"))
table_html(r$assessment, c("code", "entity_label", "entity_id"))
cat("</details>")
```

The report does not change source data, stored validation history, review
decisions, or acceptance status. Detailed network lineage and operation evidence
remain in the accompanying relation bundle/GeoPackage.
